---
title: "Inputs Layout and Forms"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Inputs Layout and Forms}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Since {shinyMobile} 2.0.0, the layout of inputs has been improved. It is recommended that multiple inputs are wrapped inside a `f7List` to benefit from styling options such as `outline`, `inset`, `strong`, and `dividers`. Also introduced since 2.0.0 are the functions `f7Form` and `updateF7Form` to gather inputs in the same form and update them in batch or only selected ones.

## Inputs Layout

Let's say you have multiple inputs, like a text input, a text area input, and a select input. You can wrap them inside a `f7List` to benefit from the styling options, styling them all at once. 

```{r, eval = FALSE}
library(shiny)
library(shinyMobile)

shinyApp(
  ui = f7Page(
    options = list(dark = FALSE,
                   theme = "ios"),
    title = "Inputs Layout",
    f7SingleLayout(
      navbar = f7Navbar(
        title = "Inputs Layout",
        hairline = FALSE
      ),
      f7List(
        inset = TRUE,
        dividers = TRUE,
        strong = TRUE,
        f7Text(
          inputId = "text",
          label = "Text input",
          value = "Some text",
          placeholder = "Your text here"
        ),
        f7TextArea(
          inputId = "textarea",
          label = "Text area input",
          value = "Some text",
          placeholder = "Your text here"
        ),
        f7Select(
          inputId = "select",
          label = "Make a choice",
          choices = 1:3,
          selected = 1
        )
      )
    )
  ),
  server = function(input, output) {
  }
)
```

By default inputs list is displayed with stacked labels. Stacked labels always appear on top of the input.

<br>

The following inputs are supported: `f7Text`, `f7TextArea`, `f7Password`, `f7Select`, `f7SmartSelect`. This doesn't mean you can't use other inputs, but they may look a bit off. In this case you can take them out of `f7List` and style them manually with the available options in the input. For example:

```{r, eval = FALSE}
library(shiny)
library(shinyMobile)

shinyApp(
  ui = f7Page(
    options = list(dark = FALSE,
                   theme = "ios"),
    title = "Inputs Layout",
    f7SingleLayout(
      navbar = f7Navbar(
        title = "Inputs Layout",
        hairline = FALSE
      ),
      f7List(
        inset = FALSE,
        dividers = TRUE,
        strong = TRUE,
        f7Text(
          inputId = "text",
          label = "Text input",
          value = "Some text",
          placeholder = "Your text here"
        ),
        f7TextArea(
          inputId = "textarea",
          label = "Text area input",
          value = "Some text",
          placeholder = "Your text here"
        ),
        f7Select(
          inputId = "select",
          label = "Make a choice",
          choices = 1:3,
          selected = 1
        )
      ),
      f7DatePicker(
        inputId = "date",
        label = "Pick a date",
        value = Sys.Date(),
        style = list(
          inset = FALSE,
          dividers = TRUE,
          strong = TRUE
        )
      ),
      f7Picker(
        inputId = "picker",
        placeholder = "Some text here!",
        label = "Picker Input",
        choices = c("a", "b", "c"),
        options = list(sheetPush = TRUE),
        style = list(
          inset = FALSE,
          dividers = TRUE,
          strong = TRUE
        )
      )
    )
  ),
  server = function(input, output) {
  }
)
```

## Forms

TODO
