---
title: "List View"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{List View}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Creating Different Types of Lists

Lists are a great way to organize information in a structured way. And Framework7 provides a number of different list types to choose from, ranging from simple text lists to more complex lists with icons, groups, headers and footers. In {shinyMobile}, all these possibilities are available through the `f7List()` and `f7ListItem()` functions.

### Styling options

There are 4 styling options available for lists:

- __inset__: to make list block inset, which will make the list block appear indented. If used in combination with strong, it will also have rounded corners.
- __outline__: to add outline (borders) around the list block
- __dividers__: to add dividers (borders) between list items
- __strong__: to add extra highlighting to list block

### Available mode options

There are 4 different modes available for lists:

- __simple__: to create a simple list
- __links__: to create a list with links
- __media__: to create a list with media elements
- __contacts__: to create a grouped list

## Examples

As you can imagine, there are a lot of possible combinations of these options. Below we will show some examples of how to create different types of lists.

### Simple list

The most simple list has `mode` set to `"simple"` and no other options set:

```{r}
library(shiny)
library(shinyMobile)

shinyApp(
  ui = f7Page(
    title = "My app",
    options = list(dark = FALSE, theme = "ios"),
    f7SingleLayout(
      navbar = f7Navbar(title = "f7List"),
      f7List(
        mode = "simple",
        lapply(1:5, function(j) {
          tags$li(
            paste("Item", j)
          )
        })
      )
    )
  ),
  server = function(input, output) {
  }
)
```

<br>

Note that we're using `tags$li()` and not `f7ListItem()` here. This is because we're creating a simple list, and `f7ListItem()` is only needed when you want to add more complex items to the list. The styling of `f7ListItem()` is also different because it adds some additional CSS classes.

<br>

Using the styling options, you can already drastically change the appearance of the list:

```{r}
library(shiny)
library(shinyMobile)

shinyApp(
  ui = f7Page(
    title = "My app",
    options = list(dark = FALSE, theme = "ios"),
    f7SingleLayout(
      navbar = f7Navbar(title = "f7List"),
      f7List(
        mode = "simple",
        outline = TRUE,
        dividers = TRUE,
        strong = TRUE,
        lapply(1:5, function(j) {
          tags$li(
            paste("Item", j)
          )
        })
      )
    )
  ),
  server = function(input, output) {
  }
)
```

### Simple link list

When setting `mode` to `"links"`, the list items will be displayed as links:

```{r}
library(shiny)
library(shinyMobile)

shinyApp(
  ui = f7Page(
    title = "My app",
    options = list(dark = FALSE, theme = "ios"),
    f7SingleLayout(
      navbar = f7Navbar(title = "f7List"),
      f7List(
        mode = "links",
        outline = TRUE,
        dividers = TRUE,
        strong = TRUE,
        lapply(1:5, function(j) {
          tags$li(
            f7Link(label = paste("Item", j), href = "https://www.google.com")
          )
        })
      )
    )
  ),
  server = function(input, output) {
  }
)
```

<br>

In the example above, we're using `f7Link()` to create the links. This will automatically make sure that the links are opened in a new tab. 

### Link list with header and footer

To add some complexity to the link list, we can add a header and footer. In this case, we will use `f7ListItem()` to create the list items. It is important to set `mode` to `NULL` in `f7List()`:   

```{r}
library(shiny)
library(shinyMobile)

shinyApp(
  ui = f7Page(
    title = "My app",
    options = list(dark = FALSE, theme = "md"),
    f7SingleLayout(
      navbar = f7Navbar(title = "f7List"),
      f7List(
        mode = NULL,
        outline = TRUE,
        dividers = TRUE,
        strong = TRUE,
        lapply(1:5, function(j) {
          f7ListItem(
            title = paste("Item", j),
            header = paste("Header", j),
            footer = paste("Footer", j),
            href = "https://www.google.com"
          )
        })
      )
    )
  ),
  server = function(input, output) {
  }
)
```

### Grouped list

### Media list

## Other Types of Lists

The list view can be used in other cases as well:

- To create a __virtual list__ with `f7VirtualList()` for displaying a list with a large number of items.
- To create an inputs layout, where inputs can be nicely grouped and styled together inside an `f7List()`. You can read more about this in the [Inputs Layout](inputs-layout.html) vignette.
- Swipeout is an extension of the list view that allows you to swipe over list elements to reveal a hidden menu with available actions. You can use `f7Swipeout()` and `f7SwipeOutItem()` for this.
