---
title: "Split-Layout"
author: "David Granjon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Split-Layout}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shinyF7)
```

`f7SplitLayout()` is the third layout introduced with shinyF7. This template is focused for 
tablet use. It is composed of a sidebar, and a main panel. The sidebar goes in its dedicated slot, corresponding to `f7Panel()`. While `f7Panel()` may also be embedded
in both `f7SingleLayout()` and `f7TabsLayout`, it accepts extra arguments like `f7PanelMenu()` and
`f7PanelItem()`, which are very similar to sidebar items of shinydashboard:

```r
f7Panel(
  title = "Sidebar",
  side = "left",
  theme = "light",
  f7PanelMenu(
    id = "menu",
    f7PanelItem(tabName = "tab1", title = "Tab 1", icon = f7Icon("email"), active = TRUE),
    f7PanelItem(tabName = "tab2", title = "Tab 2", icon = f7Icon("home"))
  ),
  style = "reveal"
)
```

The content must be passed in `...` If you have a menu in the sidebar, you must use the
corresponding body function, namely `f7Items()` and `f7Item()`. Particularly, the *tabName*
argument provided in `f7PanelItem()` and `f7Item()` must exactly match (like in shinydashboard, again).
If you don't have any `f7PanelMenu()`, you can pass tags in the `...` directly. However, 
this prevents you from having a tabbed navigation. 


<div class="marvel-device ipad black">
<div class="camera"></div>
<div class="screen">
<iframe width="100%" src="https://dgranjon.shinyapps.io/miniUI2Split" allowfullscreen="" frameborder="0" scrolling="no" height="750px"></iframe>
</div>
<div class="home"></div>
</div>


```r
library(shiny)
 library(shinyF7)
 shiny::shinyApp(
   ui = f7Page(
     title = "My app",
     #dark_mode = TRUE,
     init = f7Init(hideNavOnPageScroll = FALSE, hideTabsOnPageScroll = FALSE),
     f7SplitLayout(
       sidebar = f7Panel(
         title = "Sidebar",
         side = "left",
         theme = "light",
         f7PanelMenu(
           id = "menu",
           f7PanelItem(tabName = "tab1", title = "Tab 1", icon = f7Icon("email"), active = TRUE),
           f7PanelItem(tabName = "tab2", title = "Tab 2", icon = f7Icon("home"))
         ),
         style = "reveal"
       ),
       navbar = f7Navbar(
         title = "Split Layout",
         hairline = FALSE,
         shadow = TRUE
       ),
       toolbar = f7Toolbar(
         position = "bottom",
         f7Link(label = "Link 1", src = "https://www.google.com"),
         f7Link(label = "Link 2", src = "https://www.google.com", external = TRUE)
       ),
       # main content
       f7Items(
         f7Item(
           tabName = "tab1",
           sliderInput("obs", "Number of observations:",
                       min = 0, max = 1000, value = 500
           ),
           plotOutput("distPlot")
         ),
         f7Item(tabName = "tab2", "Tab 2 content")
       )
     )
   ),
   server = function(input, output) {

     observe({
       print(input$menu)
     })

     output$distPlot <- renderPlot({
       dist <- rnorm(input$obs)
       hist(dist)
     })
   }
 )
```
