---
title: "multipages"
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shiny)
#library(brochure)
library(shinyMobile)
```

## Introduction

Since v2.0.0, `{shinyMobile}` has __multi pages__ support. Under the hood, this amazing feature is made possible owing to the `{brochure}` [package](https://github.com/ColinFay/brochure) from 
[Colin Fay](https://github.com/ColinFay) as well as the internal Framework7 [router](https://framework7.io/docs/view).

What is multi pages navigation? If you consider a basic website with 2 pages such as `index.html` and `other.html`, browsing to `https:://mywebsite.com` opens `index.html` while typing `https:://mywebsite.com/other.html` requests the `other.html` page. If you take a classic shiny app with tabs, clicking on one tab gives you the illusion to browse to another page because of the Bootstrap JS and CSS magic. That's however not the case as the url does not change. Therefore, Shiny doesn't support multi pages navigation by default. `{brochure}` makes this somehow possible.

## About brochure

To develop a `{brochure}` app, you need the following template:

```{r, eval=FALSE}
page_1 <- function() {
  page(
    href = "/",
    ui = function(request) {
      # PAGE 1 UI
    },
    server = function(input, output, session) {
      # Server function
    }
  )
}

page_2 <- function() {
  page(
    href = "/2",
    ui = function(request) {
      # Page 2 UI
    },
    server = function(input, output, session) {
      # Server function
    }
  )
}

page_3 <- function() {
  page(
    href = "/3",
    ui = function(request) {
      # Page 3 UI
    },
    server = function(input, output, session) {
      # Server function
    }
  )
}

brochureApp(
  # Pages
  page_1(),
  page_2(),
  page_3(),
  wrapped = <WRAPPER-FUNC>
)
```

In brief, you create different pages with `page()` and put them inside `brochureApp()`. Each page is composed of a `ui`, `server` and `href` which represents the location where to serve the page. In theory, as mentionned in the `{brochure}` documentation, each page has its own shiny session, which means that if you go from page 1 to page 2, the state of page 1 is lost when you come back to it. 

For `{shinyMobile}`, we decided to slightly deviate from this and only assign a global server function, meaning that you can use the `brochureApp()` __server__ 
parameter instead of the one from `page()`. This requires to install a modified version of
`{brochure}`:

```{r, eval=FALSE}
devtools::install_github("DivadNojnarg/brochure")
```

Besides, `brochureApp()` exposes __wrapped__, allowing us to inject our own `f7MultiLayout()` function, described below with more details.

## The new f7MultiLayout

`f7MultiLayout()` accepts elements of a certain layout, similar to what is exposed by the `f7SingleLayout()`:

```{r, eval=FALSE}
shiny::tags$div(
  class = "page",
  # top navbar goes here
  f7Navbar(title = "Home page"),
  # Optional toolbar #
  tags$div(
    class = "page-content",
    ...
  )
)
```

__page__ is the main wrapper which takes a __navbar__ and __page-content__ as children. Note that you can also have a local __toolbar__, assuming you didn't define a main toolbar in `f7MultiLayout()`. Indeed, if you pass a __toolbar__ to the corresponding `f7MultiLayout()` parameter, it is seen as a global app toolbar. __page-content__ is where is displayed the page content such as `{shinyMobile}` widgets.

`f7MultiLayout()` accepts a list of app options, like `f7DefaultOptions()`, which are internally forwarded to `f7Page()`. 
At the time of writting of this vignette, you must install a patched `{brochure}` version with `devtools::install_github("DivadNojnarg/brochure")` to be able to pass custom options to `brochureApp()`, which essentially calls `do.call(wrapped, wrapped_options)`:

```{r, eval=FALSE}
brochureApp(
  # Pages
  page_1(),
  page_2(),
  page_3(),
  wrapped = <WRAPPER-FUNC>
  wrapped_options = <OPTIONS>
)
```

## Framework 7 router
Internally, `f7MultiLayout()` wraps all the pages in a __view__ reponsible for the page navigation and history (going back and forward with the browser back/next buttons). This __view__ is also called __router__. 

```{r, eval=FALSE}
# f7MultiLayout
shiny::tags$div(
  class = "view view-main view-init",
  # Base url
  `data-url` = "/",
  # Important: to be able to have updated url when changing page
  `data-browser-history` = "true",
  # Optional common toolbar
  toolbar,
  ...
)
```

In addition to creating the pages UI, we need to tell Framework7 how to route the pages. This is pretty simple, as we can pass a list of routes which is sent to JS with the app __options__ list. This may yield something like this:

```{r, eval=FALSE}
# Framework7 options: see f7DefaultOptions()
options = list(
  # dark mode option
  dark = TRUE,
  routes = list(
    list(path = "/", url = "/", name = "home"),
    # Important: don't remove keepalive
    # for child pages as this allows
    # to save the input state when switching
    # between pages. If FALSE, each time a page is
    # changed, inputs are reset (except on the first page).
    list(path = "/2", url = "/2", name = "2", keepAlive = TRUE),
    list(path = "/3", url = "/3", name = "3", keepAlive = TRUE)
  )
)
```

For each route, we must provide:

- __path__: path display in the url.
- __url__: page url. In our case, this is identical to the path.
- __keepAlive__: this ensures that when we leave the current page and come back, 
we don't lose the state of inputs and widgets inside. 
Hence, it is expected to be `TRUE`. See more [here](https://framework7.io/docs/routes#keep-alive).

## A simple multi pages app

let's build our simple app. It has 3 pages, the welcome page and 2 other 
pages. We create the navigation links as follows with the `f7Link()` function
and allowing `routable`:

```{r, eval=FALSE}
links <- lapply(2:3, function(i) {
  tags$li(
    f7Link(
      routable = TRUE,
      label = sprintf("Link to page %s", i),
      href = sprintf("/%s", i)
    )
  )
})
```

Importantly, the __href__ must point to the right location passed in the routes options, as 
previously described (here it is `/2` and `/3`).

The first page is a function wrapped by the `{brochure}` `page()` function containing:

- a __ui__ component with a navbar, the page content.
- __href__ must be `/` that is the root page.

```{r, eval=FALSE}
page_1 <- function() {
  page(
    href = "/",
    ui = function(request) {
      shiny::tags$div(
        class = "page",
        # top navbar goes here
        f7Navbar(title = "Home page"),
        tags$div(
          class = "page-content",
          f7List(
            inset = TRUE,
            strong = TRUE,
            outline = TRUE,
            dividers = TRUE,
            mode = "links",
            links
          )
        )
      )
    }
  )
}
```

`links` are wrapped within a `f7List()` which has better styling options.

The second page follows the same layout. Notice that we could pass it a local `toolbar` but 
decided to use the global toolbar from `f7Multilayout()` so all pages share the same
toolbar. This choice is up to your preference. A cool new feature from 
`{shinyMobile}` 2.0.0 is the ability to pass tags to the `f7Navbar()` __left__ parameter, which
make it possible to add a back button link:

```{r, eval=FALSE}
page_2 <- function() {
  page(
    href = "/2",
    ui = function(request) {
      shiny::tags$div(
        class = "page",
        # top navbar goes here
        f7Navbar(
          title = "Second page",
          # Allows to go back to main
          leftPanel = tags$a(
            href = "/",
            class = "link",
            tags$i(class = "icon icon-back"),
            tags$span(
              class = "if-not-md",
              "Back"
            )
          )
        ),
        # NOTE: when the main toolbar is enabled in
        # f7MultiLayout, we can't use individual page toolbars.
        # f7Toolbar(
        #  position = "bottom",
        #  tags$a(
        #    href = "/",
        #    "Main page",
        #    class = "link"
        #  )
        # ),
        shiny::tags$div(
          class = "page-content",
          f7Block(f7Button(inputId = "update", label = "Update stepper")),
          f7List(
            strong = TRUE,
            inset = TRUE,
            outline = FALSE,
            f7Stepper(
              inputId = "stepper",
              label = "My stepper",
              min = 0,
              max = 10,
              size = "small",
              value = 4,
              wraps = TRUE,
              autorepeat = TRUE,
              rounded = FALSE,
              raised = FALSE,
              manual = FALSE
            )
          ),
          verbatimTextOutput("test")
        )
      )
    }
  )
}
```

The page contains a `f7Stepper()` which is an improved numeric input.

Finally, you'll find the third page code in the global app code below.

The main server function contains all the logic related to widgets you can
find in all pages and passed to the `brochureApp()` __server__ parameter:

```{r, eval=FALSE}
server = function(input, output, session) {
  output$res <- renderText(input$text)
  output$test <- renderPrint(input$stepper)

  observeEvent(input$update, {
    updateF7Stepper(
      inputId = "stepper",
      value = 0.1,
      step = 0.01,
      size = "large",
      min = 0,
      max = 1,
      wraps = FALSE,
      autorepeat = FALSE,
      rounded = TRUE,
      raised = TRUE,
      color = "pink",
      manual = TRUE,
      decimalPoint = 2
    )
  })
}
```

Notice that the global app toolbar is passed with the __wrapper_options__
parameter, the reason being it has to be injected in the `f7MultiLayout()` wrapper:

```{r, eval=FALSE}
wrapped_options = list(
  # Common toolbar
  toolbar = f7Toolbar(
    f7Link(icon = f7Icon("house"), href = "/", routable = TRUE)
  ),
  # Other options
  ...
)
```

As you can see, that wasn't tricky to setup such a layout and the entire working example is
shown below.

<div class="text-center">
<a class="btn btn-primary" data-bs-toggle="collapse" href="#tabLayout" role="button" aria-expanded="false" aria-controls="tabLayout">
Code
</a>
</div>

<div class="collapse" id="tabLayout">
```{r, eval=FALSE}
library(shiny)
# Needs a specific version of brochure for now.
# This allows to pass wrapper functions with options
# as list. We need it because of the f7Page options parameter
# and to pass the routes list object for JS.
# devtools::install_github("DivadNojnarg/brochure")
library(brochure)
library(shinyMobile)

links <- lapply(2:3, function(i) {
  tags$li(
    f7Link(
      routable = TRUE,
      label = sprintf("Link to page %s", i),
      href = sprintf("/%s", i)
    )
  )
})

page_1 <- function() {
  page(
    href = "/",
    ui = function(request) {
      shiny::tags$div(
        class = "page",
        # top navbar goes here
        f7Navbar(title = "Home page"),
        tags$div(
          class = "page-content",
          f7List(
            inset = TRUE,
            strong = TRUE,
            outline = TRUE,
            dividers = TRUE,
            mode = "links",
            links
          )
        )
      )
    }
  )
}

page_2 <- function() {
  page(
    href = "/2",
    ui = function(request) {
      shiny::tags$div(
        class = "page",
        # top navbar goes here
        f7Navbar(
          title = "Second page",
          # Allows to go back to main
          leftPanel = tags$a(
            href = "/",
            class = "link",
            tags$i(class = "icon icon-back"),
            tags$span(
              class = "if-not-md",
              "Back"
            )
          )
        ),
        # NOTE: when the main toolbar is enabled in
        # f7MultiLayout, we can't use individual page toolbars.
        # f7Toolbar(
        #  position = "bottom",
        #  tags$a(
        #    href = "/",
        #    "Main page",
        #    class = "link"
        #  )
        # ),
        shiny::tags$div(
          class = "page-content",
          f7Block(f7Button(inputId = "update", label = "Update stepper")),
          f7List(
            strong = TRUE,
            inset = TRUE,
            outline = FALSE,
            f7Stepper(
              inputId = "stepper",
              label = "My stepper",
              min = 0,
              max = 10,
              size = "small",
              value = 4,
              wraps = TRUE,
              autorepeat = TRUE,
              rounded = FALSE,
              raised = FALSE,
              manual = FALSE
            )
          ),
          verbatimTextOutput("test")
        )
      )
    }
  )
}

page_3 <- function() {
  page(
    href = "/3",
    ui = function(request) {
      shiny::tags$div(
        class = "page",
        # top navbar goes here
        f7Navbar(
          title = "Third page",
          # Allows to go back to main
          leftPanel = tags$a(
            href = "/",
            class = "link",
            tags$i(class = "icon icon-back"),
            tags$span(
              class = "if-not-md",
              "Back"
            )
          )
        ),
        # NOTE: when the main toolbar is enabled in
        # f7MultiLayout, we can't use individual page toolbars.
        # f7Toolbar(
        #  position = "bottom",
        #  tags$a(
        #    href = "/2",
        #    "Second page",
        #    class = "link"
        #  )
        # ),
        shiny::tags$div(
          class = "page-content",
          f7Block("Nothing to show yet ...")
        )
      )
    }
  )
}

brochureApp(
  # Pages
  page_1(),
  page_2(),
  page_3(),
  # Important: in theory brochure makes
  # each page having its own shiny session/ server function.
  # That's not what we want here so we'll have
  # a global server function.
  server = function(input, output, session) {
    output$res <- renderText(input$text)
    output$test <- renderPrint(input$stepper)

    observeEvent(input$update, {
      updateF7Stepper(
        inputId = "stepper",
        value = 0.1,
        step = 0.01,
        size = "large",
        min = 0,
        max = 1,
        wraps = FALSE,
        autorepeat = FALSE,
        rounded = TRUE,
        raised = TRUE,
        color = "pink",
        manual = TRUE,
        decimalPoint = 2
      )
    })
  },
  wrapped = f7MultiLayout,
  wrapped_options = list(
    # Common toolbar
    toolbar = f7Toolbar(
      f7Link(icon = f7Icon("house"), href = "/", routable = TRUE)
    ),
    options = list(
      dark = TRUE,
      theme = "md",
      routes = list(
        list(path = "/", url = "/", name = "home"),
        # Important: don't remove keepalive
        # for child pages as this allows
        # to save the input state when switching
        # between pages. If FALSE, each time a page is
        # changed, inputs are reset (except on the first page).
        list(path = "/2", url = "/2", name = "2", keepAlive = TRUE),
        list(path = "/3", url = "/3", name = "3", keepAlive = TRUE)
      )
    )
  )
)
```
</div>

## Going further
You might find more convenient to assign a Shiny __module__
per page such as:

```{r, eval=FALSE}
page_ui <- function(id) {
  ns <- shiny::NS(id)

  tags$div(
    class = "page",
    f7Navbar(title = "Navbar"),
    tags$div(
      class = "page-content",
      f7Block(
        inset = TRUE,
        strong = TRUE,
        f7Text(ns("text"), "A text input", "Super text!"),
        textOutput(ns("res"))
      )
    )
  )
}

page_server <- function(id) {
  moduleServer(
    id, 
    function(input, output, session) {
      output$res <- renderText(input$text)
    }
  )
}

my_page <- function() {
  page(
    href = "/",
    ui = page_ui("page1")
  )
}

brochureApp(
  my_page(),
  server = function(input, output, session) {
    # Call modules here
    page_server("page1")
  },
  wrapped = f7MultiLayout,
  wrapped_options = list(
    # Common toolbar
    toolbar = f7Toolbar(
      f7Link(icon = f7Icon("house"), href = "/", routable = TRUE)
    ),
    options = list(
      dark = TRUE,
      theme = "md",
      routes = list(
        list(path = "/", url = "/", name = "home"),
        # Important: don't remove keepalive
        # for child pages as this allows
        # to save the input state when switching
        # between pages. If FALSE, each time a page is
        # changed, inputs are reset (except on the first page).
        list(path = "/2", url = "/2", name = "2", keepAlive = TRUE),
        list(path = "/3", url = "/3", name = "3", keepAlive = TRUE)
      )
    )
  )
)
```
